Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-02-26 WSSSPE1_report/WSSSPE1_summary_report.tex
spell out PDB

The first keynote~\cite{WSSSPE1-keynote1} was delivered by Philip
E. Bourne of University of California, San Diego.  Bourne is a basic
biomedical scientist but has formed four software companies. He co-founded 
PLOS Computational Biology~\cite{plos-web} and helped develop the RCSB PDB~\cite{pdb-web}.  
He is working on automating three-dimensional visualizations of cell
contents and molecular structures, a problem that has not been solved
and when done, would serve as a key function of software in biomedical
sciences.

>>>>

The first keynote~\cite{WSSSPE1-keynote1} was delivered by Philip
E. Bourne of University of California, San Diego.  Bourne is a basic
biomedical scientist but has also formed four software companies. He co-founded 
PLOS Computational Biology~\cite{plos-web} and helped develop the RCSB
Protein Data Bank~\cite{pdb-web}.  
He is working on automating three-dimensional visualizations of cell
contents and molecular structures, a problem that has not been solved
and when done, would serve as a key function of software in biomedical
sciences.
